A (sun)Shiny Recreation of the New York Times \n Weather Chart

### 2017-04-25 Paper.Rmd
image things
changing legends

text_layer_average <-  annotate("text",
                                label = "Normal range", 
                                x =  lubridate::ymd("2016-07-19"), 
                                y = 0, 
                                hjust = "right", 
                                size = 2.3)

@@

![Screenshot of Single Year Tab in Shiny App](Images/single_year_screenshot.png)

>>>>

text_layer_average <-  annotate("text",
                                label = "Range of Historical Averages", 
                                x =  lubridate::ymd("2016-07-19"), 
                                y = 0, 
                                hjust = "right", 
                                size = 2.3)

@@

```{r, fig.height = 3, fig.width = 12, warning = F, message = F, echo = F, fig.cap = "Screenshot of Single Year Tab in Shiny App"}
library(png)
library(grid)
img <- readPNG("Images/single_year_screenshot2.png")
grid.raster(img)
```
